Blind Search for 21-cm Absorption Systems in New Generation Chinese Radio Telescopes

### 2016-11-22 ms_21cm.tex
title, science goal

\title{Searching 21-cm Absorption Systems in Chinese Radio Telescopes}

@@

\abstract{
Neutral hydrogen clouds are known to exist in the Universe, however their spatial
distributions and physical properties are poorly understood. Such missing information
can be studied by the Chinese new generation radio telescopes by a blind searching
of 21-cm absorption systems. We forecast the abilities of surveys of 21-cm absorption
systems by two representative radio telescopes in China --
Five-hundred-meter Aperture Spherical radio Telescope (FAST) and
Tianlai. The result shows that, in a few of years term,
these telescopes with either high sensitivity (FAST)
or wide field of view (Tianlai) can discover orders of magnitudes
more 21-cm absorption systems, than the cumulative discoveries
in the past 50 years. 
\keywords{}
}

\authorrunning{Yu et al.}
\titlerunning{Searching 21-cm Absorption Systems}

@@

The 21-cm absorption systems are important in the study of the 
distribution, location, temperature and structure of neutral gas,
and the evolution of neutral gas systems and galaxies over
cosmic time scale.
Due to the narrow intrinsic line width, the 21-cm absorption systems
are proposed to be used to directly measure the cosmic acceleration
\citep{2012ApJ...761L..26D,2014PhRvL.113d1303Y}, via the 
Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
The uncertainties are from the poorly understood neutral hydrogen
clouds. Path finder surveys, taking less than a year, are needed
to improve our understandings of spatial distribution and physical
properties of neutral hydrogen clouds.
This can be done by the Chinese new generation radio telescopes --
Five-hundred-meter Aperture Spherical radio Telescope (FAST)
\citep{2016RaSc...51.1060L} and
Tianlai \citep{2012IJMPS..12..256C}. In the current and near future,
these are the two symbolic modern radio telescopes in China.
The single-dish FAST, like Arecibo\footnote{https://www.naic.edu},
uses its gigantic single dish to achieve ultimate sensitivity, whereas
Tianlai, designed like CHIME\footnote{http://chime.phas.ubc.ca},
has ultra wide field of view (FoV) per day, by
using its cylindrical reflectors and arrays of receivers to
scan the northern hemisphere of the sky as the Earth turns.

According to their different design and observing strategies,
we forecast their abilities of blind searching of 21-cm absorption
systems. In section \ref{sec.sensitivity} we show the sensitivity
estimation and all the aspects
needed to be taken into account,
and according to the configurations of FAST and Tianlai,
we show their forecast in section \ref{sec.FAST}
and section \ref{sec.Tianlai} respectively.
Conclusions are made in section \ref{sec.conclusion}.

\section{Sensitivity}\label{sec.sensitivity}
To find possible 21-cm absorption systems, radio telescopes
could be devised to scan the radio sources in
NRAO VLA Sky Survey (NVSS)\footnote{http://www.cv.nrao.edu/nvss/}.
If we assume the distributions of radio sources $n_R$ and
{\HI} clouds $n_{\rm \HI}$ are uniform over the sky, then the redshift
distribution of the 21-cm absorption systems $n_{\rm system}$ would be
\begin{equation}\label{eq.n_system}
    n_{\rm system}(z)=n_{\rm \HI}(z)\int_z^\infty n_R(z')\diff z'
\end{equation}
regardless of the observation sensitivity,
where $n_R(z)$ is given by equation (26) of \cite{2010A&ARv..18....1D}.
Spacial distribution of {\HI} is poorly understood and is to be
studied in upcoming surveys.
Recent studies show that the number density of
absorbers to be $\diff n_{\rm \HI}/\diff z\sim 0.045$
per line of sight
\citep{2005ARA&A..43..861W,2007ASSP....3..501Z}, so we apply this value
in the following forcast.

Observation sensitivity depends on the background fluxes and foreground
absorptions (current section), as well as telescope configurations and
observation strategies (section \ref{sec.FAST},\ref{sec.Tianlai}).

@@

FAST has a fixed 500 m dish, and a circle of 300 m diameter is held
in the correct parabolic shape, being used at any one time. This
enables its zenith angle to be $40^\circ$ and it can scan objects
in declination range $-14^\circ 12'<\delta<65^\circ 48'$.
The 19-beam feed-horn array at L band will be the primary survey
instrument for FAST. For a single day it can scan $0.762^\circ$
in declination $\delta$. FAST survey strategy scans each object
only once ($n_{\rm obs}=1$), and with its high sensitivity,
even faint sources are identified in a single day. 
We assume a one-month survey by FAST
around the celestial equator for simplicity. FAST observes
1.2 to 1.4 GHz (redshift $z_{\rm \HI}<0.2$), so objects on celestial equator
have average transit time $\Delta t \simeq 10\ {\rm sec.}$
Taking $\Delta\nu\simeq$ 9 kHz, $n_{\rm pol}=2$, and
${\rm SEFD}=1$ Jy for FAST.
we have $\Delta F \simeq\ 2.3 {\rm mJy}$.
Taking into account the $\nu^{-0.7}$ flux boost at lower
frequencies, $rF>10\Delta F$ requires $F\gtrsim 0.11\ {\rm Jy}$ on 1.4 GHz.

@@

Regarding the quantitative forecasts in each telescope, although we take
into account many detailed aspects affecting the result, the major
uncertainties are $n_{\rm \HI}(z)$, $u_{\rm width}$ and $r$.
These poorly understood parameters are conversely worth investigating
from these proposed surveys. Modest real-time analysis changes could
allow the survey of 21-cm absorption systems. The data would need to be
recorded at sufficient spectral resolution. Spatial computational costs are
in principle unchanged, but there could be additional overhead
costs for the larger resulting data sets.

>>>>

\title{Blind Search for 21-cm Absorption Systems in New Generation Chinese Radio Telescopes}

@@

\abstract{
Neutral hydrogen clouds are known to exist in the Universe, however their spatial
distributions and physical properties are poorly understood. Such missing information
can be studied by the new generation Chinese radio telescopes by a blind searching
of 21-cm absorption systems. We forecast the abilities of surveys of 21-cm absorption
systems by two representative radio telescopes in China --
Five-hundred-meter Aperture Spherical radio Telescope (FAST) and
Tianlai 21-cm cosmology experiment (Tianlai).
The result shows that, in a few of years term,
these telescopes with either high sensitivity (FAST)
or wide field of view (Tianlai) can discover orders of magnitudes
more 21-cm absorption systems, than the cumulative discoveries
in the past 50 years. 
\keywords{}
}

\authorrunning{Yu et al.}
\titlerunning{Blind Search for 21-cm Absorption Systems}

@@

The 21-cm absorption systems are important in the study of the 
distribution, location, temperature and structure of neutral gas,
and the evolution of neutral gas systems and galaxies over
cosmic time scale.
Due to the narrow intrinsic line width, the 21-cm absorption systems
are proposed to be used to directly measure the cosmic acceleration
\citep{2012ApJ...761L..26D,2014PhRvL.113d1303Y}, via the 
Sandage-Loeb (SL) effect \citep{1962ApJ...136..319S,1998ApJ...499L.111L}.
The uncertainties of these decade-long proposals are from the poorly understood
{\HI} clouds \citep{2014PhRvL.113d1303Y}.
Path finder surveys, taking less than a year, are able
to improve our understandings of spatial distribution and physical
properties of {\HI} clouds.
This can be done by the Chinese new generation radio telescopes --
Five-hundred-meter Aperture Spherical radio Telescope (FAST)
\citep{2016RaSc...51.1060L} and Tianlai 21-cm cosmology experiment
(Tianlai) \citep{2012IJMPS..12..256C}. In the current and near future,
these are the two symbolic new generation radio telescopes in China.
The single-dish FAST, like Arecibo\footnote{https://www.naic.edu},
uses its gigantic single dish to achieve ultimate sensitivity, whereas
Tianlai, designed like CHIME\footnote{http://chime.phas.ubc.ca},
has ultra wide field of view (FoV) per day, by
using its cylindrical reflectors and arrays of receivers to
scan the northern hemisphere of the sky as the Earth turns.

According to their different design and observing strategies,
we forecast their abilities of blind searching of 21-cm absorption
systems. In section \ref{sec.sensitivity} we show the sensitivity
estimation and related factors needed taken into account,
and according to the configurations of FAST and Tianlai,
we show their forecast in section \ref{sec.FAST}
and section \ref{sec.Tianlai} respectively.
Conclusions are made in section \ref{sec.conclusion}.

\section{Sensitivity}\label{sec.sensitivity}
To find possible 21-cm absorption systems, radio telescopes
could be devised to scan the radio sources in
NRAO VLA Sky Survey (NVSS)\footnote{http://www.cv.nrao.edu/nvss/}.
If we assume the distributions of radio sources $n_R$ and
{\HI} clouds $n_{\rm \HI}$ are uniform over the sky, then the redshift
distribution of the 21-cm absorption systems $n_{\rm system}$ would be
\begin{equation}\label{eq.n_system}
    n_{\rm system}(z)=n_{\rm \HI}(z)\int_z^\infty n_R(z')\diff z'
\end{equation}
regardless of the observation sensitivity,
where $n_R(z)$ is given by equation (26) of \cite{2010A&ARv..18....1D}.
Spacial distribution of {\HI} is poorly understood and is to be
studied in upcoming surveys.
Recent studies show that the number density of
absorbers to be $\diff n_{\rm \HI}/\diff z\sim 0.045$
per line of sight at low and medium redshift
\citep{2005ARA&A..43..861W,2007ASSP....3..501Z}, so we apply this value
in the following forcast.
Observation sensitivity depends on the background fluxes and foreground
absorptions (current section), as well as telescope configurations and
observation strategies (section \ref{sec.FAST},\ref{sec.Tianlai}).

@@

FAST has a fixed 500-meter-dish, and a circle of 300 meter in diameter is held
in the correct parabolic shape, being used at any one time. This
enables its zenith angle up to $40^\circ$ and it can scan objects
in declination range $-14^\circ 12'<\delta<65^\circ 48'$.
The 19-beam feed-horn array at L band will be the primary survey
instrument for FAST. For a single day it can scan total of $0.762^\circ$
in declination $\delta$. FAST survey strategy scans each object
only once ($n_{\rm obs}=1$), and with its high sensitivity,
even faint sources are identified in a single day. 
We assume a one-month survey by FAST
around the celestial equator for simplicity. FAST observes
1.2 to 1.4 GHz (redshift $z_{\rm \HI}<0.2$), so objects on celestial equator
have average transit time $\Delta t \simeq 10\ {\rm sec.}$
Taking $\Delta\nu\simeq$ 9 kHz, $n_{\rm pol}=2$
(dual polarized system), and
${\rm SEFD}=1$ Jy for FAST.
we have $\Delta F \simeq\ 2.3 {\rm mJy}$.
Taking into account the $\nu^{-0.7}$ flux boost at lower
frequencies, $rF>10\Delta F$ requires $F\gtrsim 0.11\ {\rm Jy}$ on 1.4 GHz.

@@

Regarding the quantitative forecasts in each telescope, although we take
into account many detailed aspects affecting the result, the major
uncertainties are $n_{\rm \HI}(z)$, $u_{\rm width}$ and $r$.
These poorly understood parameters are conversely worth investigating
from these proposed surveys. Modest real-time analysis changes could
allow the survey of 21-cm absorption systems. The data would need to be
recorded at sufficient spectral resolution. Spatial computational costs are
in principle unchanged, but there could be additional overhead
costs for the larger resulting data sets. Systematic surveys of
{\HI} clouds over a cosmic scale enable us to measure the 3D density
of these systems. For objects detected by FAST, one can also try to measure
the 21cm emission size. For Tianlai, one can try to measure the size from
very-long-baseline interferometry (VLBI).
